Convex Surrogates via Polyhedral Losses

### 2019-03-04 cvx-fin.tex
Went back through and checked proofs- only added thoughts as comments

\usetikzlibrary{calc}
\newcommand{\Comments}{0}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

  \cite{agarwal2015consistent} and ~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g. $0-1$ loss via their notion of feasible subspace dimension.

@@

We write loss functions as $L:\R\to\reals^\Y_+$ which map a report (prediction) $r\in\R$ to the vector of loss values $L(r) = (L(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
Often $\R$ will be taken to be a finite set for the given discrete loss (in which case we will write $\ell$ not $L$), and $\reals^d$ for the surrogate.
The expected loss of report $r$ when $y \sim p$ is written $\inprod{p}{L(r)}$.
For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$ given by $\ell(r)_y = \Ind[r \neq y]$.
Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.

@@

\begin{definition}[Finite property, non-redundant]
  A property $\Gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ we have $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
  $\Gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite.
  We typically write finite properties in lower case, as $\gamma$.
\end{definition}

Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
For example, the \emph{mode} is the property $\mode(p) = \argmax_{y\in\Y} p_y$, which is finite.
The mode captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
This terminology comes from the information elicitation literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

Often one is given a property $\gamma$ (typically via a discrete loss $\ell$) and one seeks a surrogate loss $L$ with certain attributes, such as convexity, smoothness, etc.
In doing so, we may be interested in the minimum number of dimensions needed for such an indirect elicitation scheme; this is the notion of \emph{elicitation complexity}~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
The two notions of elicitation complexity we use most are as follows: let $\eliccvx(\gamma)$ be the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a convex loss function $L: \reals^d \to \reals^\Y_+$, and $\elicpoly(\gamma)$ the minimum such $d$ where $L$ is polyhedral.
We will also discuss $\eliccts$, which is the complexity with respect to continuous, real-valued, non-locally-constant properties (\S~\ref{sec:1d}), and $\elicembed$, which is the minimum dimension for $\gamma$ to be embedded (Definition~\ref{def:embedding-dim}).

As a brief aside, we note that previous definitions of elicitation complexity have used a more straightforward link function, as the properties considered were single-valued~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
In particular, if both $\gamma$ and $\Gamma$ are single-valued, these works simply require $\gamma = f \circ \Gamma$.
When $\Gamma$ is set-valued, one still straightforwardly requires $\gamma(p) = f(u)$ for all $u \in \Gamma(p)$.
The notion of a calibrated link from Definition~\ref{def:links} is only required when both $\gamma$ and $\Gamma$ could be set-valued, as is the case in general for convex surrogates of finite properties.

@@

\begin{definition}\label{def:trim}
  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t. } \forall u'\in\R,u'\neq u,\, \Gamma_u \not\subseteq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
\end{definition}
\raft{Note for later: should be able to show that the union of trim is the simplex.}

@@

\begin{proposition}\label{prop:embed-link}
  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
  Then there is a calibrated link from $\Gamma$ to $\gamma$. % which can be taken to be separated if $L$ is polyhedral.
\end{proposition}
\begin{proof}
  Let $\gamma:\simplex\toto\R$.
  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
  We conclude that for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
  The link $\psi : \reals^d \to \R$ which encodes these choices is calibrated.
  \raft{Commented out the separated stuff}
  % Now assume $L$ is polyhedral.
  % \jessiet{Hole jere: $j$-faces of the function.}
  % For the second part of the statement, in order for $\psi$ to be separated, for $\epsilon > 0$, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
  % If the loss $L$ is polyhedral, we want to show that we can construct a $\psi$ so that the above holds.
  %
  % First, consider that each of the embedded points in $u \in \varphi(\R)$ must have ball $B(\epsilon, u)$ centered on $u$ so that no other $w \in \varphi(\R)$ is in $B(\epsilon, u)$.
  % If this is not true, then \jessie{...?} \jessiet{I'm not sure how this messes with things, but I would think the level sets corresponding to the two points would differ on a set of zero measure, if at all, or both be in the $\arginf$of the loss...?}
  %
  % Now for any $u \in \varphi(\R)$ and $v \in B(\epsilon, u)$, if $\psi(v)$ does not map to $\psi(u)$, then there must be some other $w \in \varphi(\R)$ so that $\psi(v) = \psi(w)$.
  % Since $L$ is polyhedral, we know that for $p \in \simplex$ such that $v \in \Gamma(p)$, then since $u$ and $v$ are sufficiently close, $\E_p L(w,Y) = \E_p L(v,Y) \leq \E_p L(u,Y)$.
  % However, if the inequality was strict, then we contradict the polyhedral structure of $L$, since $v$ is not an embedded point.
  % Therefore, $v \in \Gamma(p) \implies u \in \Gamma(p)$, and we can alter the link function so that $\psi(v) = \psi(u)$.
  %
  %
  % If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
%Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
%Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
%Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
\end{proof}
In typical applications, one requires more of the link, namely that it should be separated (see Definition~\ref{def:links}).
In most cases, devising a separated link is straightforward, for example with polyhedral losses using bullet 3 in Theorem~\ref{thm:finite-elicit-embed} below.
Giving a construction that yields a separated link for all polyhedral losses is a challenging open question.
\raft{Replace this paragraph with gloating about our result if we actually give this construction.}

With a solid understanding of the structure of embeddings and embeddable properties, we now turn to the relationship between embeddings and polyhedral losses.
We give a tight connection: every finite elicitable property is embedded by a polyhedral loss, and every polyhedral loss embeds a finite elicitable property.
We state this equivalence in two parts, the first focusing on the property, and the second on the loss.

\begin{theorem}\label{thm:finite-elicit-embed}
  Let $\gamma$ be a finite property.
  The following are equivalent.
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\gamma$ is elicitable.
  \item $\gamma$ is embeddable.
  \item $\gamma$ is embeddable via a polyhedral loss.
  \end{enumerate}
\end{theorem}
\begin{proof}
  We trivially have $3\Rightarrow 2$, and by Proposition~\ref{prop:embed-trim} we also have $2\Rightarrow 1$.
  It thus suffices to show $1\Rightarrow 3$.
  In fact, this direction is a corollary of a stronger result given as Theorem~\ref{thm:general-duality-embedding} in the appendix, which states as follows.
  For any non-redundant property $\gamma'$, even if not finite, elicited by a loss with a Bayes risk which is a closed function, $\gamma'$ is embeddable in $d =n-1$ dimensions.
  By Lemma~\ref{lem:finite-full-dim}, the (negative) Bayes risk $G$ of the given finite elicitable property $\gamma$ is polyhedral and therefore closed, so the theorem applies.
  Moreover, the construction given in Theorem~\ref{thm:general-duality-embedding} defines the loss embedding $\gamma$ as $L(u) = C(u)\ones - u$ where $C=G^*$ is the convex conjugate of $G$, which is also polyhedral~\citet[Theorem 19.2]{rockafellar1997convex}.
  (Here $\ones\in\reals^\Y$ denotes the all-ones vector.)
  Thus $L$ is polyhedral.
\end{proof}

We now state a converse of Theorem~\ref{thm:finite-elicit-embed}: every polyhedral loss embeds a finite elicitable property.
One way to look at this result in light of Proposition~\ref{prop:embed-trim} is that polyhedral losses ``directly'' elicit finite properties by embedding them into a space where the original loss is convex.
Moreover, we show that indirect elicitation via polyhedral losses are heavily structured: if a polyhedral loss elicits a property $\gamma'$ with a link to $\gamma$, then both $\gamma'$ and $\gamma$ are finite and one ``refines'' the other in the sense below.
In other words, the cells (level sets) of $\gamma'$ must be a finite subdivision of the cells of $\gamma$.
This fact will become useful when we discuss the relationship between embedding dimension and elicitation complexity.\raf{LATER: see [WHERE WE DISCUSS]}

@@

From Theorem~\ref{thm:1d-tfae}, we can already prove lower bounds on embedding dimension, as well as the other complexity classes mentioned.
Here are two simple examples.
\begin{corollary}
  Let $n\geq 3$ and $\alpha\in(0,1)$.  Then the following are bounded below by 2:
    $\elicembed(\abstain{\alpha})$,
    $\elicpoly(\abstain{\alpha})$,
    $\eliccvx(\abstain{\alpha})$,
    $\eliccts(\abstain{\alpha})$,
    $\elicembed(\mode)$,
    $\elicpoly(\mode)$,
    $\eliccvx(\mode)$,
    $\eliccts(\mode)$.
\end{corollary}
\begin{proof}
  % Every cell (level set) of an orderable property is adjacent to at most two other cells.
  % This fails to hold for \raf{abstain} when $n\geq 3$ and the mode when $n\geq 4$.
  % For the mode when $n=3$, we simply observe that the intersection of any two adjacent cells fails to be a hyperplane.
  The cell adjacency graph of an orderable property must be a path, but for the mode it is the complete graph on $n$ nodes, and for $\abstain{\alpha}$ a star graph on $n+1$ nodes, which are not paths when $n \geq 3$.
\end{proof}

@@

\begin{definition}\label{def:d-construction}
  Given a polytope $\{p \in \Delta_{\Y} : Bp \geq 0\}$ for $B \in \reals^{k \times n}$, a \emph{$d$-construction} of it is a $V \in \reals^{k \times d}$ such that, for each column $B_i$ of $B$, the pair $(V,B_i)$ is a tight halfspace representation.
\end{definition}

@@

\paragraph{Other necessary conditions.}
One can also derive other kinds of potentially necessary conditions from the general characterization in Theorem \ref{thm:char}.
One is related to the weak monotonicity property of convex functions.\bo{raf please fill in}
Another is a reduction to the one-dimensional characterization. If one considers any embedded property in $\reals^d$ and restricts the report space to a line while keeping the loss the same, one obtains a new $1$-dimensional embedded property.
Picking a line that e.g. goes through previous embedding or indifference points, those that were optimal originally must still be optimal under the same distribution.
At this point, the one-dimensional characterization may rule out embeddability.

\subsection{Example}
We give an example of how this necessary condition can be applied to prove a lower bound.
The \emph{abstain property} sets a threshold of $\alpha$ (here, $\alpha=0.5$) and has $\R = \Y \cup \{\text{abstain}\}$.
We have $\text{abstain} \in \gamma(p) \iff \max_y p_y \leq \alpha$, and $y \in \gamma(p) \iff p_y = \max_{y'} p_{y'}, p_y \geq \alpha$.
In other words, it is similar to the mode, except that if none of the options has a high enough probability, the best report is to abstain.
\citet{ramaswamy2018consistent} show that this property on $|\Y|=n$ can be embedded in $\lceil \log_2(n) \rceil$ dimensions.
Their construction is quite beautiful and extremely instructive for studying embeddings.
In particular, it shows how to embed abstain$(0.5)$ on $4$ outcomes into $\reals^2$.
Prior to this work, it was not known if one could improve by embedding abstain($0.5$) for $5$ or more outcomes in $\reals^2$.

@@

\bo{A whole section of the following proof can be cut out, but it's trying to be a tutorial. Pairs well with the figure}
\begin{theorem}\label{thm:abs-5outcome-not-2embed}
  Abstain with $\alpha=1/2$ and $|\Y|=5$ is not $2$-embeddable.
\end{theorem}

@@

\paragraph{Implications.}
We conjecture that the construction of \citet{ramaswamy2018consistent} is optimal in all dimensions.
If so, this leaves two possibilities: It might be that there is some \emph{non-embedding} approach that elicits this property using a report space of fewer than $d=\lceil \log_2 |\Y|\rceil$ dimensions.
Going beyond the embedding approach seems to require new ideas that could be relevant to many applications in machine learning.
On the other hand, it might be that the best possible dimension is achieved by an embedding approach and polyhedral loss.
If true, it would be interesting to see how generally this might hold.
\begin{conjecture}\label{conj:abstain-tight}
  Abstain with $\alpha=1/2$ is $(\log_2 |\Y|)$-embeddable, but no lower.
\end{conjecture}

@@

\section{To Sort}

Several definitions from \citet{aurenhammer1987power}.
\begin{definition}\label{def:cell-complex}
  A \emph{cell complex} in $\reals^d$ is a set $C$ of faces (of dimension $0,\ldots,d$) which (i) union to $\reals^d$, (ii) have pairwise disjoint relative interiors, and (iii) any nonempty intersection of faces $F,F'$ in $C$ is a face of $F$ and $F'$ and an element of $C$.
\end{definition}

@@

\begin{lemma}\label{lem:polyhedral-pd-same}
  Let $f_1,\ldots,f_k:\reals^d\to\reals$ be polyhedral convex functions.
  The power diagram induced by $\sum_{i=1}^k p_i f_i$ is the same for all $p \in \inter\simplex$.
\end{lemma}
\begin{proof}
  For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
  Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
  It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter F'$ with constant derivative $d\in\reals^d$.
  Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.

>>>>

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

  \cite{agarwal2015consistent} and ~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g. \jessiet{take out of math mode} $0-1$ loss via their notion of feasible subspace dimension.

@@

We write loss functions as $L:\R\to\reals^\Y_+$ which map a report (prediction) $r\in\R$ to the vector of loss values $L(r) = (L(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
Often $\R$ will be taken to be a finite set for the given discrete loss (in which case we will write $\ell$ not $L$), and $\reals^d$ for the surrogate.
The expected loss of report $r$ when $y \jessie{Y} \sim p$ is written $\inprod{p}{L(r)}$.
For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$ given by $\ell(r)_y = \Ind[r \neq y]$.
Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.

@@

\begin{definition}[Finite property, non-redundant]
  A property $\Gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ we have $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
  $\Gamma$ is \emph{finite} if it is non-redundant and $\R$ is \jessiet{delete: a} a finite.
  We typically write finite properties in lower case, as $\gamma$.
\end{definition}

Thus, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
For example, the \emph{mode} is the property $\mode(p) = \argmax_{y\in\Y} p_y$, which is finite.
The mode captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
This terminology comes from the information elicitation \jessiet{information vs property... do we care?} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

Often one is given a property $\gamma$ (typically via a discrete loss $\ell$) and \jessiet{delete: one} one seeks a surrogate loss $L$ with certain attributes, such as convexity, smoothness, etc.
In doing so, we may be interested in the minimum number of dimensions needed for such an indirect elicitation scheme; this is the notion of \emph{elicitation complexity}~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
The two notions of elicitation complexity we use most are as follows: let $\eliccvx(\gamma)$ be the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a convex loss function $L: \reals^d \to \reals^\Y_+$, and $\elicpoly(\gamma)$ the minimum such $d$ where $L$ is polyhedral.
We will also discuss $\eliccts$, which is the complexity with respect to continuous, real-valued, non-locally-constant properties (\S~\ref{sec:1d}), and $\elicembed$, which is the minimum dimension for $\gamma$ to be embedded (Definition~\ref{def:embedding-dim}).

As a brief aside, we note that previous definitions of elicitation complexity have used a more straightforward link function, as the properties considered were single-valued~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
In particular, if both $\gamma$ and $\Gamma$ are single-valued, these works simply require $\gamma = f \circ \Gamma$. \jessiet{What is $f$?  Not defined...}
When $\Gamma$ is set-valued, one still straightforwardly requires $\gamma(p) = f(u)$ for all $u \in \Gamma(p)$.
The notion of a calibrated link from Definition~\ref{def:links} is only required when both $\gamma$ and $\Gamma$ could be set-valued, as is the case in general for convex surrogates of finite properties.

@@

\begin{definition}\label{def:trim}
  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t. } \forall u'\in\R,u'\neq u,\, \Gamma_u \not\subseteq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
\end{definition}
\jessiet{What if $\Gamma_u = \Gamma_{u'}$?  Wouldn't we remove both copies of the level set as is?}
\raft{Note for later: should be able to show that the union of trim is the simplex.}

@@

\begin{proposition}\label{prop:embed-link}
  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
  Then there is a calibrated link from $\Gamma$ to $\gamma$. % which can be taken to be separated if $L$ is polyhedral.
\end{proposition}
\begin{proof}
  Let $\gamma:\simplex\toto\R$.
  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
  \jessiet{Delete: ``We conclude that ''}
  We conclude that for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
  The link $\psi : \reals^d \to \R$ which encodes these choices is calibrated.
  \raft{Commented out the separated stuff}
  % Now assume $L$ is polyhedral.
  % \jessiet{Hole jere: $j$-faces of the function.}
  % For the second part of the statement, in order for $\psi$ to be separated, for $\epsilon > 0$, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
  % If the loss $L$ is polyhedral, we want to show that we can construct a $\psi$ so that the above holds.
  %
  % First, consider that each of the embedded points in $u \in \varphi(\R)$ must have ball $B(\epsilon, u)$ centered on $u$ so that no other $w \in \varphi(\R)$ is in $B(\epsilon, u)$.
  % If this is not true, then \jessie{...?} \jessiet{I'm not sure how this messes with things, but I would think the level sets corresponding to the two points would differ on a set of zero measure, if at all, or both be in the $\arginf$of the loss...?}
  %
  % Now for any $u \in \varphi(\R)$ and $v \in B(\epsilon, u)$, if $\psi(v)$ does not map to $\psi(u)$, then there must be some other $w \in \varphi(\R)$ so that $\psi(v) = \psi(w)$.
  % Since $L$ is polyhedral, we know that for $p \in \simplex$ such that $v \in \Gamma(p)$, then since $u$ and $v$ are sufficiently close, $\E_p L(w,Y) = \E_p L(v,Y) \leq \E_p L(u,Y)$.
  % However, if the inequality was strict, then we contradict the polyhedral structure of $L$, since $v$ is not an embedded point.
  % Therefore, $v \in \Gamma(p) \implies u \in \Gamma(p)$, and we can alter the link function so that $\psi(v) = \psi(u)$.
  %
  %
  % If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
%Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
%Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
%Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
\end{proof}
In typical applications, one requires more of the link, namely that it should be separated (see Definition~\ref{def:links}).
In most cases, devising a separated link is straightforward, for example with polyhedral losses using bullet 3 in Theorem~\ref{thm:finite-elicit-embed} below.
Giving a construction that yields a separated link for all polyhedral losses is a challenging open question.
\raft{Replace this paragraph with gloating about our result if we actually give this construction.}

With a solid understanding of the structure of embeddings and embeddable properties, we now turn to the relationship between embeddings and polyhedral losses.
We give a tight connection: every finite elicitable property is embedded by a polyhedral loss, and every polyhedral loss embeds a finite elicitable property.
We state this equivalence in two parts, the first focusing on the property, and the second on the loss.
\jessiet{I'm guessing the statement changed after this was written, but three parts?}

\begin{theorem}\label{thm:finite-elicit-embed}
  Let $\gamma$ be a finite property.
  The following are equivalent.
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\gamma$ is elicitable.
  \item $\gamma$ is embeddable.
  \item $\gamma$ is embeddable via a polyhedral loss.
  \end{enumerate}
\end{theorem}
\begin{proof}
  We trivially have $3\Rightarrow 2$, and by Proposition~\ref{prop:embed-trim} we also have $2\Rightarrow 1$.
  It thus suffices to show $1\Rightarrow 3$.
  In fact, this direction is a corollary of a stronger result given as Theorem~\ref{thm:general-duality-embedding} in the appendix, which states as follows.
  \jessiet{Is the end of this sentence grammatically correct?}
  For any non-redundant property $\gamma'$, even if not finite, elicited by a loss with a Bayes risk which is a closed function, $\gamma'$ is embeddable in $d =n-1$ dimensions.
  By Lemma~\ref{lem:finite-full-dim}, the (negative) Bayes risk $G$ of the given finite elicitable property $\gamma$ is polyhedral and therefore closed, so the theorem applies.
  Moreover, the construction given in Theorem~\ref{thm:general-duality-embedding} defines the loss embedding $\gamma$ as $L(u) = C(u)\ones - u$ where $C=G^*$ is the convex conjugate of $G$, which is also polyhedral~\citet[Theorem 19.2]{rockafellar1997convex}.
  (Here $\ones\in\reals^\Y$ denotes the all-ones vector.)
  Thus $L$ is polyhedral.
\end{proof}

We now state a converse of Theorem~\ref{thm:finite-elicit-embed}: every polyhedral loss embeds a finite elicitable property.
One way to look at this result in light of Proposition~\ref{prop:embed-trim} is that polyhedral losses ``directly'' elicit finite properties by embedding them into a space where the original loss is convex.
Moreover, we show that indirect elicitation via polyhedral losses are heavily structured: if a polyhedral loss elicits a property $\gamma'$ with a link to $\gamma$, then both $\gamma'$ and $\gamma$ are finite and one ``refines'' the other in the sense below.
\jessiet{Is $\gamma'$ actually finite by our definition, or is it ``finite-ish'', i.e. finite if we ignore a null set of distributions?}
In other words, the cells (level sets) of $\gamma'$ must be a finite subdivision of the cells of $\gamma$.
This fact will become useful when we discuss the relationship between embedding dimension and elicitation complexity.\raf{LATER: see [WHERE WE DISCUSS]}

\jessiet{Any reason we go from $\gamma$ and $\gamma'$ to $\Gamma$ and $\Gamma'$ from paragraph to definition?}

@@

From Theorem~\ref{thm:1d-tfae}, we can already prove lower bounds on embedding dimension, as well as the other complexity classes mentioned.
Here are two simple examples.
\begin{corollary}
  Let $n\geq 3$ and $\alpha\in(0,1)$.  Then the following are bounded below by 2:
    $\elicembed(\abstain{\alpha})$,
    $\elicpoly(\abstain{\alpha})$,
    $\eliccvx(\abstain{\alpha})$,
    $\eliccts(\abstain{\alpha})$,
    $\elicembed(\mode)$,
    $\elicpoly(\mode)$,
    $\eliccvx(\mode)$,
    $\eliccts(\mode)$.
\end{corollary}
\jessiet{Can we separate the abstain and mode by a new line so they kind of line up?  Or just write it a more elegant way than exhaustive?}
\begin{proof}
  % Every cell (level set) of an orderable property is adjacent to at most two other cells.
  % This fails to hold for \raf{abstain} when $n\geq 3$ and the mode when $n\geq 4$.
  % For the mode when $n=3$, we simply observe that the intersection of any two adjacent cells fails to be a hyperplane.
  The cell adjacency graph of an orderable property must be a path, but for the mode it is the complete graph on $n$ nodes, and for $\abstain{\alpha}$ a star graph on $n+1$ nodes, which are not paths when $n \geq 3$.
\end{proof}

@@

\begin{definition}\label{def:d-construction}
  Given a polytope $\{p \in \Delta_{\Y} : Bp \geq 0\}$ for $B \in \reals^{k \times n}$, a \emph{$d$-construction} of it is a $V \in \reals^{k \times d}$ such that, for each column $B_i$ of $B$, the pair $(V,B_i)$ is a tight halfspace representation.
  \jessiet{Should we mention the known results that elicitable properties have convex level sets, and such a convex polytope exists (and in fact describes the level set) before the definition?}
\end{definition}

@@

\paragraph{Other necessary conditions.}
One can also derive other kinds of potentially necessary conditions from the general characterization in Theorem \ref{thm:char}.
One is related to the weak monotonicity property of convex functions.\bo{raf please fill in}
Another is a reduction to the one-dimensional characterization. If one considers any embedded property in $\reals^d$ and restricts the report space to a line while keeping the loss the same, one obtains a new $1$-dimensional embedded property.
\jessiet{Does the original property refine of the restricted property?  If so, that might be worth mentioning.}
Picking a line that e.g. goes through previous embedding or indifference points, those that were optimal originally must still be optimal under the same distribution.
At this point, the one-dimensional characterization may rule out embeddability.

\subsection{Example}
We give an example of how this necessary condition can be applied to prove a lower bound.
\jessiet{Throughout: find/replace 0.5 with 1/2.}
The \emph{abstain property} sets a threshold of $\alpha$ (here, $\alpha=0.5$) and has $\R = \Y \cup \{\text{abstain}\}$.
We have $\text{abstain} \in \gamma(p) \iff \max_y p_y \leq \alpha$, and $y \in \gamma(p) \iff p_y = \max_{y'} p_{y'}, p_y \geq \alpha$.
In other words, it is similar to the mode, except that if none of the options has a high enough probability, the best report is to abstain.
\jessiet{Would it be helpful to have drawings of the [3-outcome] simplex for abstain(1/2) and mode to see the difference?}
\citet{ramaswamy2018consistent} show that this property on $|\Y|=n$ can be embedded in $\lceil \log_2(n) \rceil$ dimensions.
Their construction is quite beautiful and extremely instructive for studying embeddings.
In particular, it shows how to embed abstain$(0.5)$ on $4$ outcomes into $\reals^2$.
Prior to this work, it was not known if one could improve by embedding abstain($0.5$) for $5$ or more outcomes in $\reals^2$.

@@

\begin{theorem}\label{thm:abs-5outcome-not-2embed}
  Abstain with $\alpha=1/2$ and $|\Y|=5$ is not $2$-embeddable.
\end{theorem}

@@

\paragraph{Implications.}
We conjecture that the construction of \citet{ramaswamy2018consistent} is optimal in all dimensions.
If so, this leaves two possibilities: It might be that there is some \emph{non-embedding} approach that elicits this property using a report space of fewer than $d=\lceil \log_2 |\Y|\rceil$ dimensions.
Going beyond the embedding approach seems to require new ideas that could be relevant to many applications in machine learning.
On the other hand, it might be that the best possible dimension is achieved by an embedding approach and polyhedral loss.
If true, it would be interesting to see how generally this might hold.
\begin{conjecture}\label{conj:abstain-tight}
  Abstain with $\alpha=1/2$ is $(\log_2 |\Y|)$-embeddable, but no lower.
  \jessiet{Add the ceil macros}
\end{conjecture}

@@

\section{To Sort}
\jessiet{Lol we should probably change the name of this}
Several definitions from \citet{aurenhammer1987power}.
\begin{definition}\label{def:cell-complex}
  A \emph{cell complex} in $\reals^d$ is a set $C$ of faces (of dimension $0,\ldots,d$) which (i) union to $\reals^d$, (ii) have pairwise disjoint relative interiors, and (iii) any nonempty intersection of faces $F,F'$ in $C$ is a face of $F$ and $F'$ and an element of $C$.
\end{definition}

@@

\begin{lemma}\label{lem:polyhedral-pd-same}
  Let $f_1,\ldots,f_k:\reals^d\to\reals$ be polyhedral convex functions.
  \jessiet{Replace $k$ with $m$?}
  The power diagram induced by $\sum_{i=1}^k p_i f_i$ is the same for all $p \in \inter\simplex$.
\end{lemma}
\begin{proof}
  For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
  Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
  It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter F'$ with constant derivative $d\in\reals^d$.
  Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.
